---
title: "Coding Challenge 6"
author: "Prativa Chhetri and Karamjit Kaur Baryah"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: gfm
  html_document:
    toc: true
    toc_float: true
  pdf_document:
    toc: true
  word_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)# For data visualization
library(drc)  # For dose-response curve analysis
library(tidyverse)  # A collection of data science packages
library(dplyr)
```


# Question 1

- reducing the chance of errors from manual repetition.

- Custom functions make your code more organized and reusable.

- If a built-in function changes in future versions of R or a package update alters behavior, your custom function ensures stability

- Writing your own functions allows you to tailor calculations, data transformations, or iterations to specific requirements.


# Question 2

(A) Writing a Function in R

A function in R is a reusable block of code that takes inputs (arguments), processes them, and returns an output. Functions help keep code organized, reusable, and easier to debug.

Syntax

$$my_function = function(arg1, arg2) {

result = arg1 + arg2 # Perform operation

return(result) # Return output

}$$


How it Works:

- Define the function with function().

- Inside {}, write the code to process inputs.

- Use return() to output a value (if omitted, R returns the last evaluated expression).

- Call the function like this:



$$my_function(3, 5) # should return to 8$$


(B) Writing a for Loop in R

A for loop in R repeats a block of code for each value in a sequence (like a vector).


Syntax
$$
for (i in 1:5) {

print(i) # Prints numbers 1 to 5

}
$$

How it Works:

- for (i in sequence): Iterates over each value in sequence.

- Inside {}, write the code that executes on each iteration.

- The loop stops when all values in sequence are processed.

$$squares = c()

for (i in 1:5) {

squares[i] = i^2 # Store squared values

}

print(squares) # Returns [1] 1 4 9 16 25 $$




# Question 3

```{r}
cities <- read.csv("Cities.csv")
head(cities)
```



# Question 4

```{r}
haversine_distance <- function(lat1, lon1, lat2, lon2) {
  rad.lat1 <- lat1 * pi / 180
  rad.lon1 <- lon1 * pi / 180
  rad.lat2 <- lat2 * pi / 180
  rad.lon2 <- lon2 * pi / 180
  
  delta_lat <- rad.lat2 - rad.lat1
  delta_lon <- rad.lon2 - rad.lon1
  a <- sin(delta_lat / 2)^2 + cos(rad.lat1) * cos(rad.lat2) * sin(delta_lon / 2)^2
  c <- 2 * asin(sqrt(a))
  
  earth_radius <- 6378137  # in meters
  distance_km <- (earth_radius * c) / 1000
  
  return(distance_km)
}
```


# Question 5 

```{r}
# Filter data for Auburn, AL and New York City
auburn <- cities %>% filter(city == "Auburn")
nyc <- cities %>% filter(city == "New York")

# Compute distance between Auburn, AL and New York City
distance_nyc_auburn <- haversine_distance(auburn$lat, auburn$long, nyc$lat, nyc$long)
print(distance_nyc_auburn)

```


```{r}

results <- data.frame(City1 = character(), City2 = character(), Distance_km = numeric(), stringsAsFactors = FALSE)

for (i in 1:nrow(cities)) {
  city <- cities[i, ]
  if (city$city != "Auburn") {
    dist <- haversine_distance(auburn$lat, auburn$long, city$lat, city$long)
    results <- rbind(results, data.frame(City1 = city$city, City2 = "Auburn", Distance_km = dist))
  }
}
print(head(results))


```




